### 2023-12-04 chapter_1/src/manuscript.qmd
closing up some drafting for today

While there are some differences between these models, they also agree on foundational perspectives of how memory is used to generate attitudes. The first is the perspective that information is organized in a schema. This conceptualization borrows significantly from the perspective that the brain is organized as a set of associated nodes in a network. This perspective has been a powerful perspective in a number of fields that study cognition. In this perspective, the cognition works because we have nodes which identify a particular piece of information. These nodes are connected to each other in a mental schema. Or some structured organization of information or memories. These connections between nodes, however are not equally strong. Rather, the strength of these nodes depend on a variety of features. Though the memory and online model vary in which features matter for influencing the strength of these nodes, they still consider the influence of activated confounding information that can make some of these connections between nodes more relevant than others. As a result, both models suggest that we do not just gather information and then just calculate the average between a pros and cons list. Rather, the degree to which a new node is added and used in the future depends on which nodes it is attached to when being encoded as memory.

>>>>

While there are some differences between these models, they also agree on foundational perspectives of how memory is used to generate attitudes. The first is the perspective that information is organized in a schema. This conceptualization borrows significantly from the perspective that the brain is organized as a set of associated nodes in a network [@collins_spreading-activation_1975]. This perspective has been a powerful perspective in a number of fields that study cognition. In this perspective, the cognition works because we have nodes which identify a particular piece of information. These nodes are connected to each other in a mental schema; or some structured organization of information or memories. These connections between nodes, however are not equally strong. Rather, the strength of these nodes depend on a variety of features. Though the memory and online model vary in which features matter for influencing the strength of these nodes, they still consider the influence of activated confounding information that can make some of these connections between nodes more relevant than others. As a result, both models suggest that we do not just gather information and then just calculate the average between a pros and cons list. Rather, the degree to which a new node is added and used in the future depends on which nodes it is attached to when being encoded as memory.

For the purposes of this project, a key commonality between these models is that they are theorizing about how pre-conscious cognitive processes not only shape how we interpret our political world but also how these processes shape how we react to this political reality. These models are widely cited and inform most contemporary political psychology. One way in which we can build upon the impact of these models is to consider forms of information that are perhaps more common than text or persuasive arguments provided political elites is by adjusting these models to account for visual information. Many of the fundamentals present in these models are necessary to theorize about visual information. However, making slight adjustments to consider the temporal ordering of what types of information are processed first has significant implications for how we understand what influences our understanding of the political world and how the public come to express an attitude.

## A theory of how visual information matters to politics
